The paper on \Large \bf Blockchain Front-running

### 2018-09-18 frontrunning/Latex/sections/abstract.tex
[frontrunning] Abstract and minor changes

% !TEX root = ../main.tex
\begin{abstract}

Abstract goes here.

>>>>

% !TEX root = ../main.tex

\begin{abstract}

We consider \textit{Front-running} to be any course of action during which an entity benefits from prior access to privileged market information about upcoming transactions and trades. Front-running has been an issue in traditional financial instrument markets since 70's. Lately, with the advent of the blockchain technology, front-running resurfaced in new forms, due to decentralization and transparency.
In this paper, we consider instances of front-running across the top 25 decentral applications (DApps) deployed on Ethereum. Additionally, we carry out detailed analysis of Status.im Initial Coin Offering (ICO) and show evidence of abnormal miner's behaviour indicative of front-running token purchases.  
Furthermore, we introduce a framework for categorizing proposed solutions to front-running and examine the applicability to the identified issues.

### 2018-09-18 frontrunning/Latex/sections/paper.tex
[frontrunning] Abstract and minor changes

Defining what exactly was considered illegal front-running required more knowledge of how these new markets behaved. \textit{CBoE} and other exchanges (and brokers) issued educational circulars for their members asserting that front-running violates existing rules, with some examples of what is considered front-running. However, the difference of opinion regarding the unfairness of front-running activities, insufficient exchange rules and lack of a precise definition in this area resulted in no action by self-regulator organizations~cite{sec1978optionsmarket}.

>>>>

Defining what exactly was considered illegal front-running required more knowledge of how these new markets behaved. \textit{CBoE} and other exchanges (and brokers) issued educational circulars for their members asserting that front-running violates existing rules, with some examples of what is considered front-running. However, the difference of opinion regarding the unfairness of front-running activities, insufficient exchange rules and lack of a precise definition in this area resulted in no action by self-regulator organizations~\cite{sec1978optionsmarket}.
